---
title: "DSC465 - Data Visualization Project"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(viridis)
library(dataMaid)
library(DataExplorer)
require(readxl)
require(tidyverse)
library(data.table)
```

### Winter 2020

### By Traffic Predictors 
#### Team Members: Naga Viraja Chunduru, Hetal Modi, Chris Figy, Lorraine (Lynne) Kriho, Rauf Nugmanov 

## 100 Level Code: Data Exploration and Data Preparation Work

### Create a sample file for each month.

#### One month 2 gb files can be downloaded from:
#### Each month has 8-9 million rides.

```{r}
#set new directory
setwd("~/Class/Winter/DataViz/Project/data (full months)")
#import 1 month of coc data
coc <- read_csv("10Oct2019_Full.csv")
```
Summary of the data:
```{r}
head(coc)

summary(coc)

```

#### Below samples a one month load of data into a 4000 random sample
```{r}
#Sample the months dataset and save a sample to the folder
#str(df)
set.seed(10)
coc_table <- data.table(coc)
coc_sample <- coc_table[sample(.N, 4000)]
write.csv(coc_sample,"~/Class/Winter/DataViz/Project/data samples/10Oct2019_.csv", row.names = FALSE)
```

Explore the Data Sample
```{r}
#Explore the Data Sample
summary(coc_sample)
#Get a high-level overview of the data using DataExplorer
#create_report(coc_sample)
```


```{r}
#create a list of the files from your target directory
lst <- list.files(path="~/Class/Winter/DataViz/Project/data samples")

#lst <- c("3mar2019.csv","4apr2019.csv","5may2019.csv","6jun2019.csv")
path = getwd()
fullpath<-paste(path,"/data samples/", lst[1], sep="")
fullpath
total <- data.frame()

for (vr in lst) {
  
  print(vr)
  fullpath<-paste(path,"/data samples/", vr, sep="")
  fullpath
  print("Reading...")
  print(fullpath)
  temp<- read.csv(fullpath)
  df<-data.frame(temp)
  total <- rbind(total, df)
  
}
write.csv(total,file = "full2019.csv")

```

```{r}
#Tip verse Distance

ggplot (coc_sample, aes(x=coc_sample$Fare, y=Tip)) +geom_point()

ggplot (coc_sample, aes(x=Tip)) +geom_histogram()

ggplot (coc_sample, aes(x=coc_sample$`Shared Trip Authorized`, y=Tip))+ geom_boxplot()

ggplot (coc_sample, aes(x=coc_sample$`Trip Start Timestamp`, y=`Trip Total`))+ geom_col()


```

```{r}
#
```





