---
title: "Data Viz Project - 200"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## RideShare Map Traffic Density in Downtown Chicago

### Import City of Chicago Sample Data from 100 Level Code 
#####  You will need to populate the google api with your key

```{r include=FALSE}
library(lubridate)
library(ggplot2)
library(dplyr)
library(data.table)
library(ggrepel)
library(tidyverse)
library(dataMaid)
library(DataExplorer)
library(janitor)
library(lubridate)
library(Hmisc)
library(outliers)
library(FactoMineR)
library(factoextra)
library(corrplot)

#Load the library
library("ggmap")
#Set your API Key
myKey = "{Your Key Here}"
ggmap::register_google(key = myKey)


```

#### Import data file created from 100 level code which pulls from city of chicago (coc) 
```{r}
#set new directory
setwd("~/Class/Winter/DataViz/Project/")
#import data
coc <- read_csv("full2019.csv")

summary(coc)

```

```{r include=FALSE}
#Get the latest Install
#if(!requireNamespace("devtools")) install.packages("devtools")
#devtools::install_github("dkahle/ggmap", ref = "tidyup", force=TRUE)

```

## Pick-Up Density

Now let's look at all the pick-up locations:
```{r}
# Chicago = 41.8781째 N, -87.6298째 W
p <-ggmap(get_googlemap(center = c(lon = -87.629800, lat =41.878100 ),
                    zoom = 11, scale = 2,
                    maptype ='roadmap',
                    color = 'color', key = myKey))

p + geom_point(aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude), data = coc, size = 0.7) +
  theme(legend.position="bottom")

```

### Drop-Off Density 
Now let's look at all the drop-off locations:
```{r}

d <-ggmap(get_googlemap(center = c(lon = -87.629800, lat =41.878100 ),
                    zoom = 11, scale = 2,
                    maptype ='terrain',
                    color = 'color', key = myKey))

d + geom_point(aes(x = Dropoff.Centroid.Longitude, y = Dropoff.Centroid.Latitude), data = coc, size = 0.7) +
  theme(legend.position="bottom")

```
#########
#REPEAT ABOVE WITH ZOOM
#########
### Pick-Up Density

Now let's look at all the pick-up locations:
```{r}
# Chicago = 41.8781째 N, -87.6298째 W
p <-ggmap(get_googlemap(center = c(lon = -87.629800, lat =41.878100 ),
                    zoom = 12, scale = 2,
                    maptype ='terrain',
                    color = 'color', key = myKey))

p + geom_point(aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude), data = coc, size = 0.7) +
  theme(legend.position="bottom")

```

### Drop-Off Density 
Now let's look at all the drop-off locations:
```{r}
d <-ggmap(get_googlemap(center = c(lon = -87.629800, lat =41.878100 ),
                    zoom = 14, scale = 2,
                    maptype ='terrain',
                    color = 'color', key = myKey))

d + geom_point(aes(x = Dropoff.Centroid.Longitude, y = Dropoff.Centroid.Latitude), data = coc, size = 0.7) +
  theme(legend.position="bottom")

```

It is a bit tricky to see the density of the pickup and dropoffs because all the points are sitting on top of each other.  Below sets the alpha variable which will make the dots transparent.  This helps display the density of points plotted.  

```{r}
p +   geom_point(aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude), colour = '#011f4b', data = coc, alpha=0.25, size = 0.5) + 
  theme(legend.position="none")
```  
  
  
```{r}
p + stat_density2d(
    aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude,
        fill = ..level.., alpha = 0.15), size = 0.01, bins = 30,
    data = coc, geom = "polygon") #+
  #geom_point(aes(x = x, y = y, stroke = 2), colour=col4, data = n, size =1.5) + 
  #geom_label_repel(aes(x, y, label = label), data=n, family = 'Times', size = 3, box.padding = 0.2, point.padding = 0.3, segment.color = 'grey50') 


```
  
  
```{r}

p + stat_density2d(
    aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude, fill = ..level.., alpha = 0.25),
    size = 0.1, bins = 40, data = coc,
    geom = "polygon"
  ) +
  geom_density2d(data = coc, 
               aes(x = Pickup.Centroid.Longitude, y = Pickup.Centroid.Latitude), size = 0.3)

```
  
## Move this to user interaction shiny application  
  
##### I'm going to move this code to a shiny app so one can see the map change by selecting an hour of the day. 
  
  
#END